Michael Croteau

### 2024-04-12 team/junior/jacqueline-zheng.qmd
update team page

---
title: "Jacqueline Zheng"
subtitle: "Undergraduate practicum student"
image: jacqueline-zheng.jpg
sortby: 6
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

>>>>

---
title: "Jacqueline Zheng"
subtitle: "Undergraduate research assistant"
image: jacqueline-zheng.jpg
sortby: 6
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

### 2024-04-12 team/junior/michael-croteau.qmd
update team page

---
title: "Michael Croteau"
subtitle: "Undergraduate practicum student"
image: michael-croteau.jpg
sortby: 6
started: "January 2024"
about:
  id: hero-heading
  template: solana
---

>>>>

---
title: "Michael Croteau"
subtitle: "Undergraduate research assistant"
image: michael-croteau.jpg
sortby: 6
started: "January 2024"
about:
  id: hero-heading
  template: solana
---
